Compositional equivalences based on Open pNets

### 2021-10-01 2016-Weak-FH-Bisim/WeakBisim.tex
a paragraph on difference with process algebras

@@

>>>>

\paragraph{What is new about open automata bisimulation?}

@@

Compositionality of bisimulation in our model come from the specification of the interactions, including actions of the holes. In pNets synchronisation vectors define the possible interactions between the pNet that fills the hole and the surrounding pNets. In open automata, this is reflected by symbolic hypotheses that depend on the actions of the holes. This additional specification is the price to pay to obtain the compositionality of bisimulation that cannot be guaranteed in traditional process algebras.

This approach also allows us to specify a sufficient condition on allowed transitions to make weak bisimulation compositional; namely it is not possible to synchronise on invisible actions from the holes or prevent them to occur.
